Clinician Scheduler Documentation

### 2019-01-24 docs/build/latex/ClinicianScheduler.tex
Work on `Scheduling` section and add `Authentication` section in manual

\begin{sphinxShadowBox}
\sphinxstyletopictitle{Contents:}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{index:id2}}{\hyperref[\detokenize{index:setup}]{\sphinxcrossref{Setup}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{index:id3}}{\hyperref[\detokenize{index:generating-google-api-credentials}]{\sphinxcrossref{Generating Google API credentials}}}

@@

\item {} 
\phantomsection\label{\detokenize{index:id4}}{\hyperref[\detokenize{index:usage}]{\sphinxcrossref{Usage}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{index:id5}}{\hyperref[\detokenize{index:clinician-configuration}]{\sphinxcrossref{Clinician Configuration}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{index:id6}}{\hyperref[\detokenize{index:adding-a-new-clinician}]{\sphinxcrossref{Adding a new clinician}}}

\item {} 
\phantomsection\label{\detokenize{index:id7}}{\hyperref[\detokenize{index:deleting-an-existing-clinician}]{\sphinxcrossref{Deleting an existing clinician}}}

\item {} 
\phantomsection\label{\detokenize{index:id8}}{\hyperref[\detokenize{index:editing-an-existing-clinician}]{\sphinxcrossref{Editing an existing clinician}}}

\item {} 
\phantomsection\label{\detokenize{index:id9}}{\hyperref[\detokenize{index:saving-the-configuration-to-a-file}]{\sphinxcrossref{Saving the configuration to a file}}}

\item {} 
\phantomsection\label{\detokenize{index:id10}}{\hyperref[\detokenize{index:loading-a-configuration-file}]{\sphinxcrossref{Loading a configuration file}}}

@@

\item {} 
\phantomsection\label{\detokenize{index:id11}}{\hyperref[\detokenize{index:google-calendar-configuration}]{\sphinxcrossref{Google Calendar Configuration}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{index:id12}}{\hyperref[\detokenize{index:creating-a-calendar}]{\sphinxcrossref{Creating a calendar}}}

\item {} 
\phantomsection\label{\detokenize{index:id13}}{\hyperref[\detokenize{index:adding-holiday-events}]{\sphinxcrossref{Adding holiday events}}}

\item {} 
\phantomsection\label{\detokenize{index:id14}}{\hyperref[\detokenize{index:adding-clinician-requests}]{\sphinxcrossref{Adding clinician requests}}}

@@

\item {} 
\phantomsection\label{\detokenize{index:id15}}{\hyperref[\detokenize{index:scheduling}]{\sphinxcrossref{Scheduling}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{index:id16}}{\hyperref[\detokenize{index:id1}]{\sphinxcrossref{Loading a configuration file}}}

\item {} 
\phantomsection\label{\detokenize{index:id17}}{\hyperref[\detokenize{index:generating-a-schedule}]{\sphinxcrossref{Generating a schedule}}}

\item {} 
\phantomsection\label{\detokenize{index:id18}}{\hyperref[\detokenize{index:exporting-a-schedule}]{\sphinxcrossref{Exporting a schedule}}}

\item {} 
\phantomsection\label{\detokenize{index:id19}}{\hyperref[\detokenize{index:publishing-a-schedule-to-google-calendar}]{\sphinxcrossref{Publishing a schedule to Google Calendar}}}

@@

\section{Clinician Configuration}
\label{\detokenize{index:clinician-configuration}}
Before we can generate a schedule, we need to create a configuration file
that specifies which clinicians are available, and how many weeks each
clinician should fulfill.

@@

\subsection{Adding clinician requests}
\label{\detokenize{index:adding-clinician-requests}}

@@

\subsection{Loading a configuration file}
\label{\detokenize{index:id1}}

\subsection{Generating a schedule}
\label{\detokenize{index:generating-a-schedule}}

@@

\subsection{Publishing a schedule to Google Calendar}
\label{\detokenize{index:publishing-a-schedule-to-google-calendar}}

>>>>

\begin{sphinxShadowBox}
\sphinxstyletopictitle{Contents:}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{index:id7}}{\hyperref[\detokenize{index:setup}]{\sphinxcrossref{Setup}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{index:id8}}{\hyperref[\detokenize{index:generating-google-api-credentials}]{\sphinxcrossref{Generating Google API credentials}}}

@@

\item {} 
\phantomsection\label{\detokenize{index:id9}}{\hyperref[\detokenize{index:usage}]{\sphinxcrossref{Usage}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{index:id10}}{\hyperref[\detokenize{index:authentication}]{\sphinxcrossref{Authentication}}}

\item {} 
\phantomsection\label{\detokenize{index:id11}}{\hyperref[\detokenize{index:clinician-configuration}]{\sphinxcrossref{Clinician Configuration}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{index:id12}}{\hyperref[\detokenize{index:adding-a-new-clinician}]{\sphinxcrossref{Adding a new clinician}}}

\item {} 
\phantomsection\label{\detokenize{index:id13}}{\hyperref[\detokenize{index:deleting-an-existing-clinician}]{\sphinxcrossref{Deleting an existing clinician}}}

\item {} 
\phantomsection\label{\detokenize{index:id14}}{\hyperref[\detokenize{index:editing-an-existing-clinician}]{\sphinxcrossref{Editing an existing clinician}}}

\item {} 
\phantomsection\label{\detokenize{index:id15}}{\hyperref[\detokenize{index:saving-the-configuration-to-a-file}]{\sphinxcrossref{Saving the configuration to a file}}}

\item {} 
\phantomsection\label{\detokenize{index:id16}}{\hyperref[\detokenize{index:loading-a-configuration-file}]{\sphinxcrossref{Loading a configuration file}}}

@@

\item {} 
\phantomsection\label{\detokenize{index:id17}}{\hyperref[\detokenize{index:google-calendar-configuration}]{\sphinxcrossref{Google Calendar Configuration}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{index:id18}}{\hyperref[\detokenize{index:creating-a-calendar}]{\sphinxcrossref{Creating a calendar}}}

\item {} 
\phantomsection\label{\detokenize{index:id19}}{\hyperref[\detokenize{index:adding-holiday-events}]{\sphinxcrossref{Adding holiday events}}}

\item {} 
\phantomsection\label{\detokenize{index:id20}}{\hyperref[\detokenize{index:adding-clinician-requests}]{\sphinxcrossref{Adding clinician requests}}}

@@

\item {} 
\phantomsection\label{\detokenize{index:id21}}{\hyperref[\detokenize{index:scheduling}]{\sphinxcrossref{Scheduling}}}
\begin{itemize}
\item {} 
\phantomsection\label{\detokenize{index:id22}}{\hyperref[\detokenize{index:id4}]{\sphinxcrossref{Loading a configuration file}}}

\item {} 
\phantomsection\label{\detokenize{index:id23}}{\hyperref[\detokenize{index:generating-a-schedule}]{\sphinxcrossref{Generating a schedule}}}

\item {} 
\phantomsection\label{\detokenize{index:id24}}{\hyperref[\detokenize{index:exporting-a-schedule}]{\sphinxcrossref{Exporting a schedule}}}

\item {} 
\phantomsection\label{\detokenize{index:id25}}{\hyperref[\detokenize{index:publishing-a-schedule-to-google-calendar}]{\sphinxcrossref{Publishing a schedule to Google Calendar}}}

@@

\section{Authentication}
\label{\detokenize{index:authentication}}\label{\detokenize{index:id1}}
When the scheduler first makes a connection to Google calendar, it needs
to create an authentication token, which will be used to simplify future
connections.

This requires you to allow the scheduler application to access a calendar
that you specified. You may encounter this when using any functionality that
interacts with Google calendar, for example in {\hyperref[\detokenize{index:generating-a-schedule}]{\sphinxcrossref{\DUrole{std,std-ref}{Generating a schedule}}}}
or in {\hyperref[\detokenize{index:publishing-a-schedule-to-google-calendar}]{\sphinxcrossref{\DUrole{std,std-ref}{Publishing a schedule to Google Calendar}}}}.

1. The scheduler should have automatically opened the access request page
in a browser window, in which case you can skip to step 2. \sphinxstylestrong{Otherwise},
locate the command prompt for the scheduler. You should see instructions
to open the access request printed on the command prompt. Follow these instructions
in order to open the access request page manually.

2. Follow the instructions on the access request page in order to allow
the scheduler application to read/write from/to the calendar you specified.
\sphinxstylestrong{(Optional)} If you opened the access request manually in step 1, you will
receive an authentication code which needs to be pasted into the command prompt

3. Once you have completed the authentication process, the scheduler will
automatically resume its functionality.

\section{Clinician Configuration}
\label{\detokenize{index:clinician-configuration}}\label{\detokenize{index:id2}}
Before we can generate a schedule, we need to create a configuration file
that specifies which clinicians are available, and how many weeks each
clinician should fulfill.

@@

\subsection{Adding clinician requests}
\label{\detokenize{index:adding-clinician-requests}}\label{\detokenize{index:id3}}

@@

\subsection{Loading a configuration file}
\label{\detokenize{index:id4}}
From the scheduling tab, click on \sphinxtitleref{Load} and select the configuration
file that you generated in {\hyperref[\detokenize{index:clinician-configuration}]{\sphinxcrossref{\DUrole{std,std-ref}{Clinician Configuration}}}}

\begin{figure}[htbp]
\centering
\sphinxhref{\_static/images/scheduling/load\_config/load\_config.png}{\sphinxincludegraphics{{load_config}.png}}\end{figure}

\subsection{Generating a schedule}
\label{\detokenize{index:generating-a-schedule}}\label{\detokenize{index:id5}}\begin{enumerate}
\item {} 
Enter the calendar year for the schedule that you want to generate.

2. \sphinxstylestrong{(Optional)} In order to retrieve the time-off requests that were populated
in Google calendar in {\hyperref[\detokenize{index:adding-clinician-requests}]{\sphinxcrossref{\DUrole{std,std-ref}{Adding clinician requests}}}}, we need to specify the
calendar ID. Open the calendar in your browser, and navigate to the
\sphinxtitleref{Settings and sharing} page.
On the setting page, navigate to the \sphinxtitleref{Integrate calendar} section, and copy
the value under \sphinxtitleref{Calendar ID} to your clipboard.
Paste this value into the \sphinxtitleref{Google Calendar ID} textbox on the \sphinxtitleref{Scheduler}
tab.

3. \sphinxstylestrong{(Optional)} If you supplied a calendar ID in step 2, you can configure
the options \sphinxtitleref{Retrieve Time-off Requests} and \sphinxtitleref{Retrieve Long Weekends} as necessary.
Enabling \sphinxtitleref{Retrieve Time-off Requests} will read the time-off calendar events
from the calendar specified in \sphinxtitleref{Calendar ID}, while enabling
\sphinxtitleref{Retrieve Long Weekends} will read the holiday events from that calendar.

4. \sphinxstylestrong{(Optional)} In the case that you only need to generate a schedule for
a subset of the calendar year, you can select the amount of blocks you need
to generate by specifying a value in \sphinxtitleref{Number of Blocks}. By default, the
scheduler will generate a full schedule, corresponding to 26 blocks.

5. Click on \sphinxtitleref{Generate}, and after a few moments you should see a preview of
the generated schedule in the table. \sphinxstylestrong{(Optional)} See {\hyperref[\detokenize{index:authentication}]{\sphinxcrossref{\DUrole{std,std-ref}{Authentication}}}}
in case you encounter problems with Google calendar at this stage.

\begin{sphinxadmonition}{note}{Note:}
It is possible that the scheduler will not be able to come up with a
schedule that satisfies your constraints. You can try adjusting
some constraints by changing the minimum and maximum number of blocks of
clinicians in the configuration file. See {\hyperref[\detokenize{index:clinician-configuration}]{\sphinxcrossref{\DUrole{std,std-ref}{Clinician Configuration}}}}
for more information on changing the configuration file.
\end{sphinxadmonition}

@@

\subsection{Publishing a schedule to Google Calendar}
\label{\detokenize{index:publishing-a-schedule-to-google-calendar}}\label{\detokenize{index:id6}}
